Countermeasures against co-location attempts in the cloud

### 2015-04-13 paper.tex
finish some stuff-

\hyphenation{op-tical net-works semi-con-duc-tor}
\IEEEoverridecommandlockouts
\begin{document}

@@

\author{\IEEEauthorblockN{Dolan Murvihill, Nathan Wells
}
\IEEEauthorblockA{Worcester Polytechnic Institute, 
Worcester, MA 01609, USA\\
Email: \texttt{\{dm, nhwells\}@wpi.edu}
}}
\maketitle

@@

\begin{itemize}
  \item Amazon's EC2 service is very popular and used for by variety of customers, some of which have sensitive data.
  \item This makes VMs on EC2 a worthwhile target.
  \item Ristenpart et al. have demonstrated that it is possible to create a VM co-resident with a target instance and
    that existing side-channel attacks can be employed against co-resident instances on the cloud.
  \item We expect that Amazon has since adjusted their VM location algorithms to make the Ristenpart attack more
    difficult. We would like to confirm that these changes have been made, by repeating the Ristenpart attack.
  \item If time permits, we will attempt to defeat Amazon's new countermeasures, or improve on the reliability of the
    Ristenpart attack, whatever is more appropriate.
\end{itemize}

\section{Background}\label{sec:background}
\todo{You should find and describe related work early on. Know what other people have done.}

@@

\bibliographystyle{IEEEtran}

\end{document}

>>>>

\hyphenation{op-tical net-works semi-con-duc-tor}
\IEEEoverridecommandlockouts

\input{preamble}

\begin{document}

@@

\author{\IEEEauthorblockN{Dolan Murvihill, Nathan Wells
}
\IEEEauthorblockA{Worcester Polytechnic Institute, 
Worcester, MA 01609, USA\\
Email: \texttt{\{dm, nhwells\}@wpi.edu}
}}
\maketitle
\nocite{*}

@@

\begin{itemize}
  \item Amazon's EC2 service is very popular and used for by variety of customers, some of which have sensitive data.
  \item This makes VMs on EC2 a worthwhile target.
  \item Ristenpart et al. have demonstrated that it is possible to create a VM co-resident with a target instance and
    that existing side-channel attacks can be employed against co-resident instances on the cloud.
  \item We expect that Amazon has since adjusted their VM location algorithms to make the Ristenpart attack more
    difficult. We would like to assess the current viability of the Ristenpart attack on today's AWS.
\end{itemize}

\section{Background}\label{sec:background}
The idea of performing cryptanalytic attacks against co-located virtual machines was discussed by Ristenpart, Shacham,
  and Savage in 2009 \cite{ristenpart09}.
They measure co-location success rates in Amazon Web Services (AWS), and suggest some potential attacks against
  co-located VMs.
Zhang \cite{zhang2014cross} et al. presented a cross-VM attack using Ristenpart's attack which was able to recover an El Gamal key across
Xen VMs.
Irazoqui, Inci, Eisenbarth, and Sunar \cite{irazoquis2014wait} then presented a practical, fast, and realistic full key
  recovery against AES across virtual machines, based on Bernstein's \cite{bernstein2005cache} attack.

Research into co-location attacks and cross-VM attacks continues to be an active research area.

@@

\bibliographystyle{IEEEtran}
\bibliography{bibliography}
\end{document}
